Hierarchical Principal Manifold Estimation

### 2023-08-13 paper/main.tex
Updates from Overleaf
add start of varying-coefficient model explanation

>>>>

The optimal value of $\lambda$ can be found using cross-validation. The solutions to this minimization problem suffice for estimating $f_{ij}(\mathbf{y})$, in which the coefficients are not time-varying. To reach estimates for the varying-coefficient models, the above minimization problem is solved for the data available within the relevant grouping at each time point. These estimates are then used to generate a new set of outcome values $\left\{\mathbf{x}'\right\}$ that correspond to a new set of parameters, $\left\{\mathbf{y}'\right\}$, which are evenly spaced throughout the estimated parameter space. The spline function is reestimated $\left\{\mathbf{x}'\right\}$ and $\left\{\mathbf{y}'\right\}$, which serve as common knots that allow the spline coefficients to be compared across time points.

The coefficients found at each time point $t$, $\mathbf{s}_t$ and $\mathbf{\alpha}_t$ are concatenated in matrix $\mathbf{\omega}_t = \left(\mathbf{s}_t^T, \mathbf{\alpha}_t^T\right)$. This coefficient matrix is then used as the output value in a cubic smoothing spline function using the time points as input values.
